---
title: "Wordle Duplicates"
author: "Olivia Weisiger"
date: '`r format(Sys.Date(), '%D')`'
output: html_document
---

### Valid Guesses

Words that are valid guesses, but will not be the final solution. Good guesses 
can give information about what letters appear in a word, and in what position.

```{r}
guesses <- read.csv("/Users/oliviaweisiger/Desktop/DataRes/valid_guesses.csv")
```

### Valid Solutions

A list of potential solutions to the Wordle puzzle. 

```{r}
solutions <- read.csv("/Users/oliviaweisiger/Desktop/DataRes/valid_solutions.csv")
```

### Finding Duplicate Proportions

Let the duplicate proportion for each specific letter be:

P(duplicate) = (# words with duplicates of letter) / (total # words with letter)

```{r}
proportions_df <- data.frame(matrix(ncol = 2, nrow = length(letters)))
#provide column names
colnames(proportions_df) <- c('letter', 'proportion')
proportions_df[, 1] <- letters
  
words_vector <- solutions[, 1] 

### checks if word is duplicate
check_duplicate <- function(word) {
  word <- unlist(strsplit(word, split = ""))
  check = FALSE
  for (i in seq_len(5)) {
    if (any(word[i] == word[-i])) {
      check = TRUE
    }
  }
  check
}

########## a ###################################################################
### checks if word has specific letter
check_a <- function(word) {
  check = FALSE
  word <- unlist(strsplit(word, split = ""))
  if ("a" %in% word) {
    check = TRUE
  }
  check
}
### finds a words
a_words <- words_vector[vapply(words_vector, check_a, logical(1))]

a_words_not_correct <- a_words[vapply(a_words, check_duplicate, logical(1))]
### checks if it has duplicate of specific letter
check_a_duplicate <- function(word) {
  check = FALSE
  word <- unlist(strsplit(word, split = ""))
  if (sum(word == "a") > 1) {
    check = TRUE
  }
  check
}
### function that checks if word is duplicate and has specific letter
check_both <- function(word) {
  check = FALSE
  if (check_duplicate(word) && check_a_duplicate(word)) {
    check = TRUE
  }
  check
}
### finds proportion
a_prop <- length(a_words[vapply(a_words, check_both, logical(1))]) / length(a_words)
### adds proportion to df
proportions_df[1 , 2] <- a_prop

############ b #################################################################

### checks if word has specific letter
check_b <- function(word) {
  check = FALSE
  word <- unlist(strsplit(word, split = ""))
  if ("b" %in% word) {
    check = TRUE
  }
  check
}

b_words <- words_vector[vapply(words_vector, check_b, logical(1))]

b_words_not_correct <- b_words[vapply(b_words, check_duplicate, logical(1))]

### checks if it has duplicate of specific letter
check_b_duplicate <- function(word) {
  check = FALSE
  word <- unlist(strsplit(word, split = ""))
  if (sum(word == "b") > 1) {
    check = TRUE
  }
  check
}

### function that checks if word is duplicate and has specific letter
check_b_both <- function(word) {
  check = FALSE
  if (check_duplicate(word) && check_b_duplicate(word)) {
    check = TRUE
  }
  check
}

### finds proportion
b_prop <- length(b_words[vapply(b_words, check_b_both, logical(1))]) / length(b_words)

### adds proportion to df
proportions_df[2 , 2] <- b_prop

############ c #################################################################

### checks if word has specific letter
check_c <- function(word) {
  check = FALSE
  word <- unlist(strsplit(word, split = ""))
  if ("c" %in% word) {
    check = TRUE
  }
  check
}

c_words <- words_vector[vapply(words_vector, check_c, logical(1))]

c_words_not_correct <- c_words[vapply(c_words, check_duplicate, logical(1))]

### checks if it has duplicate of specific letter
check_c_duplicate <- function(word) {
  check = FALSE
  word <- unlist(strsplit(word, split = ""))
  if (sum(word == "c") > 1) {
    check = TRUE
  }
  check
}

### function that checks if word is duplicate and has specific letter
check_c_both <- function(word) {
  check = FALSE
  if (check_duplicate(word) && check_c_duplicate(word)) {
    check = TRUE
  }
  check
}

### finds proportion
c_prop <- length(c_words[vapply(c_words, check_c_both, logical(1))]) / length(c_words)

### adds proportion to df
proportions_df[3 , 2] <- c_prop

############ d #################################################################

### checks if word has specific letter
check_d <- function(word) {
  check = FALSE
  word <- unlist(strsplit(word, split = ""))
  if ("d" %in% word) {
    check = TRUE
  }
  check
}

d_words <- words_vector[vapply(words_vector, check_d, logical(1))]

d_words_not_correct <- d_words[vapply(d_words, check_duplicate, logical(1))]

### checks if it has duplicate of specific letter
check_d_duplicate <- function(word) {
  check = FALSE
  word <- unlist(strsplit(word, split = ""))
  if (sum(word == "d") > 1) {
    check = TRUE
  }
  check
}

### function that checks if word is duplicate and has specific letter
check_d_both <- function(word) {
  check = FALSE
  if (check_duplicate(word) && check_d_duplicate(word)) {
    check = TRUE
  }
  check
}

### finds proportion
d_prop <- length(d_words[vapply(d_words, check_d_both, logical(1))]) / length(d_words)

### adds proportion to df
proportions_df[4 , 2] <- d_prop

############ e #################################################################

### checks if word has specific letter
check_e <- function(word) {
  check = FALSE
  word <- unlist(strsplit(word, split = ""))
  if ("e" %in% word) {
    check = TRUE
  }
  check
}

e_words <- words_vector[vapply(words_vector, check_e, logical(1))]

e_words_not_correct <- e_words[vapply(e_words, check_duplicate, logical(1))]

### checks if it has duplicate of specific letter
check_e_duplicate <- function(word) {
  check = FALSE
  word <- unlist(strsplit(word, split = ""))
  if (sum(word == "e") > 1) {
    check = TRUE
  }
  check
}

### function that checks if word is duplicate and has specific letter
check_e_both <- function(word) {
  check = FALSE
  if (check_duplicate(word) && check_e_duplicate(word)) {
    check = TRUE
  }
  check
}

### finds proportion
e_prop <- length(e_words[vapply(e_words, check_e_both, logical(1))]) / length(e_words)

### adds proportion to df
proportions_df[5 , 2] <- e_prop

############ f #################################################################

### checks if word has specific letter
check_f <- function(word) {
  check = FALSE
  word <- unlist(strsplit(word, split = ""))
  if ("f" %in% word) {
    check = TRUE
  }
  check
}

f_words <- words_vector[vapply(words_vector, check_f, logical(1))]

f_words_not_correct <- f_words[vapply(f_words, check_duplicate, logical(1))]

### checks if it has duplicate of specific letter
check_f_duplicate <- function(word) {
  check = FALSE
  word <- unlist(strsplit(word, split = ""))
  if (sum(word == "f") > 1) {
    check = TRUE
  }
  check
}

### function that checks if word is duplicate and has specific letter
check_f_both <- function(word) {
  check = FALSE
  if (check_duplicate(word) && check_f_duplicate(word)) {
    check = TRUE
  }
  check
}

### finds proportion
f_prop <- length(f_words[vapply(f_words, check_f_both, logical(1))]) / length(f_words)

### adds proportion to df
proportions_df[6 , 2] <- f_prop

############ g #################################################################

### checks if word has specific letter
check_g <- function(word) {
  check = FALSE
  word <- unlist(strsplit(word, split = ""))
  if ("g" %in% word) {
    check = TRUE
  }
  check
}

g_words <- words_vector[vapply(words_vector, check_g, logical(1))]

g_words_not_correct <- g_words[vapply(g_words, check_duplicate, logical(1))]

### checks if it has duplicate of specific letter
check_g_duplicate <- function(word) {
  check = FALSE
  word <- unlist(strsplit(word, split = ""))
  if (sum(word == "g") > 1) {
    check = TRUE
  }
  check
}

### function that checks if word is duplicate and has specific letter
check_g_both <- function(word) {
  check = FALSE
  if (check_duplicate(word) && check_g_duplicate(word)) {
    check = TRUE
  }
  check
}

### finds proportion
g_prop <- length(g_words[vapply(g_words, check_g_both, logical(1))]) / length(g_words)

### adds proportion to df
proportions_df[7 , 2] <- g_prop

############ h #################################################################

### checks if word has specific letter
check_h <- function(word) {
  check = FALSE
  word <- unlist(strsplit(word, split = ""))
  if ("h" %in% word) {
    check = TRUE
  }
  check
}

h_words <- words_vector[vapply(words_vector, check_h, logical(1))]

h_words_not_correct <- h_words[vapply(h_words, check_duplicate, logical(1))]

### checks if it has duplicate of specific letter
check_h_duplicate <- function(word) {
  check = FALSE
  word <- unlist(strsplit(word, split = ""))
  if (sum(word == "h") > 1) {
    check = TRUE
  }
  check
}

### function that checks if word is duplicate and has specific letter
check_h_both <- function(word) {
  check = FALSE
  if (check_duplicate(word) && check_h_duplicate(word)) {
    check = TRUE
  }
  check
}

### finds proportion
h_prop <- length(h_words[vapply(h_words, check_h_both, logical(1))]) / length(h_words)

### adds proportion to df
proportions_df[8 , 2] <- h_prop

############ i #################################################################

### checks if word has specific letter
check_i <- function(word) {
  check = FALSE
  word <- unlist(strsplit(word, split = ""))
  if ("i" %in% word) {
    check = TRUE
  }
  check
}

i_words <- words_vector[vapply(words_vector, check_i, logical(1))]

i_words_not_correct <- i_words[vapply(i_words, check_duplicate, logical(1))]

### checks if it has duplicate of specific letter
check_i_duplicate <- function(word) {
  check = FALSE
  word <- unlist(strsplit(word, split = ""))
  if (sum(word == "i") > 1) {
    check = TRUE
  }
  check
}

### function that checks if word is duplicate and has specific letter
check_i_both <- function(word) {
  check = FALSE
  if (check_duplicate(word) && check_i_duplicate(word)) {
    check = TRUE
  }
  check
}

### finds proportion
i_prop <- length(i_words[vapply(i_words, check_i_both, logical(1))]) / length(i_words)

### adds proportion to df
proportions_df[9 , 2] <- i_prop

############ j #################################################################

### checks if word has specific letter
check_j <- function(word) {
  check = FALSE
  word <- unlist(strsplit(word, split = ""))
  if ("j" %in% word) {
    check = TRUE
  }
  check
}

j_words <- words_vector[vapply(words_vector, check_j, logical(1))]

j_words_not_correct <- j_words[vapply(j_words, check_duplicate, logical(1))]

### checks if it has duplicate of specific letter
check_j_duplicate <- function(word) {
  check = FALSE
  word <- unlist(strsplit(word, split = ""))
  if (sum(word == "j") > 1) {
    check = TRUE
  }
  check
}

### function that checks if word is duplicate and has specific letter
check_j_both <- function(word) {
  check = FALSE
  if (check_duplicate(word) && check_j_duplicate(word)) {
    check = TRUE
  }
  check
}

### finds proportion
j_prop <- length(j_words[vapply(j_words, check_j_both, logical(1))]) / length(j_words)

### adds proportion to df
proportions_df[10 , 2] <- j_prop

############ k #################################################################

### checks if word has specific letter
check_k <- function(word) {
  check = FALSE
  word <- unlist(strsplit(word, split = ""))
  if ("k" %in% word) {
    check = TRUE
  }
  check
}

k_words <- words_vector[vapply(words_vector, check_k, logical(1))]

k_words_not_correct <- k_words[vapply(k_words, check_duplicate, logical(1))]

### checks if it has duplicate of specific letter
check_k_duplicate <- function(word) {
  check = FALSE
  word <- unlist(strsplit(word, split = ""))
  if (sum(word == "k") > 1) {
    check = TRUE
  }
  check
}

### function that checks if word is duplicate and has specific letter
check_k_both <- function(word) {
  check = FALSE
  if (check_duplicate(word) && check_k_duplicate(word)) {
    check = TRUE
  }
  check
}

### finds proportion
k_prop <- length(k_words[vapply(k_words, check_k_both, logical(1))]) / length(k_words)

### adds proportion to df
proportions_df[11 , 2] <- k_prop

############ l #################################################################

### checks if word has specific letter
check_l <- function(word) {
  check = FALSE
  word <- unlist(strsplit(word, split = ""))
  if ("l" %in% word) {
    check = TRUE
  }
  check
}

l_words <- words_vector[vapply(words_vector, check_l, logical(1))]

l_words_not_correct <- l_words[vapply(l_words, check_duplicate, logical(1))]

### checks if it has duplicate of specific letter
check_l_duplicate <- function(word) {
  check = FALSE
  word <- unlist(strsplit(word, split = ""))
  if (sum(word == "l") > 1) {
    check = TRUE
  }
  check
}

### function that checks if word is duplicate and has specific letter
check_l_both <- function(word) {
  check = FALSE
  if (check_duplicate(word) && check_l_duplicate(word)) {
    check = TRUE
  }
  check
}

### finds proportion
l_prop <- length(l_words[vapply(l_words, check_l_both, logical(1))]) / length(l_words)

### adds proportion to df
proportions_df[12 , 2] <- l_prop

############ m #################################################################

### checks if word has specific letter
check_m <- function(word) {
  check = FALSE
  word <- unlist(strsplit(word, split = ""))
  if ("m" %in% word) {
    check = TRUE
  }
  check
}

m_words <- words_vector[vapply(words_vector, check_m, logical(1))]

m_words_not_correct <- m_words[vapply(m_words, check_duplicate, logical(1))]

### checks if it has duplicate of specific letter
check_m_duplicate <- function(word) {
  check = FALSE
  word <- unlist(strsplit(word, split = ""))
  if (sum(word == "m") > 1) {
    check = TRUE
  }
  check
}

### function that checks if word is duplicate and has specific letter
check_m_both <- function(word) {
  check = FALSE
  if (check_duplicate(word) && check_m_duplicate(word)) {
    check = TRUE
  }
  check
}

### finds proportion
m_prop <- length(m_words[vapply(m_words, check_m_both, logical(1))]) / length(m_words)

### adds proportion to df
proportions_df[13 , 2] <- m_prop

############ n #################################################################

### checks if word has specific letter
check_n <- function(word) {
  check = FALSE
  word <- unlist(strsplit(word, split = ""))
  if ("n" %in% word) {
    check = TRUE
  }
  check
}

n_words <- words_vector[vapply(words_vector, check_n, logical(1))]

n_words_not_correct <- n_words[vapply(n_words, check_duplicate, logical(1))]

### checks if it has duplicate of specific letter
check_n_duplicate <- function(word) {
  check = FALSE
  word <- unlist(strsplit(word, split = ""))
  if (sum(word == "n") > 1) {
    check = TRUE
  }
  check
}

### function that checks if word is duplicate and has specific letter
check_n_both <- function(word) {
  check = FALSE
  if (check_duplicate(word) && check_n_duplicate(word)) {
    check = TRUE
  }
  check
}

### finds proportion
n_prop <- length(n_words[vapply(n_words, check_n_both, logical(1))]) / length(n_words)

### adds proportion to df
proportions_df[14 , 2] <- n_prop

############ o #################################################################

### checks if word has specific letter
check_o <- function(word) {
  check = FALSE
  word <- unlist(strsplit(word, split = ""))
  if ("o" %in% word) {
    check = TRUE
  }
  check
}

o_words <- words_vector[vapply(words_vector, check_o, logical(1))]

o_words_not_correct <- o_words[vapply(o_words, check_duplicate, logical(1))]

### checks if it has duplicate of specific letter
check_o_duplicate <- function(word) {
  check = FALSE
  word <- unlist(strsplit(word, split = ""))
  if (sum(word == "o") > 1) {
    check = TRUE
  }
  check
}

### function that checks if word is duplicate and has specific letter
check_o_both <- function(word) {
  check = FALSE
  if (check_duplicate(word) && check_o_duplicate(word)) {
    check = TRUE
  }
  check
}

### finds proportion
o_prop <- length(o_words[vapply(o_words, check_o_both, logical(1))]) / length(o_words)

### adds proportion to df
proportions_df[15 , 2] <- o_prop

############ p #################################################################

### checks if word has specific letter
check_p <- function(word) {
  check = FALSE
  word <- unlist(strsplit(word, split = ""))
  if ("p" %in% word) {
    check = TRUE
  }
  check
}

p_words <- words_vector[vapply(words_vector, check_p, logical(1))]

p_words_not_correct <- p_words[vapply(p_words, check_duplicate, logical(1))]

### checks if it has duplicate of specific letter
check_p_duplicate <- function(word) {
  check = FALSE
  word <- unlist(strsplit(word, split = ""))
  if (sum(word == "p") > 1) {
    check = TRUE
  }
  check
}

### function that checks if word is duplicate and has specific letter
check_p_both <- function(word) {
  check = FALSE
  if (check_duplicate(word) && check_p_duplicate(word)) {
    check = TRUE
  }
  check
}

### finds proportion
p_prop <- length(p_words[vapply(p_words, check_p_both, logical(1))]) / length(p_words)

### adds proportion to df
proportions_df[16 , 2] <- p_prop

############ q #################################################################

### checks if word has specific letter
check_q <- function(word) {
  check = FALSE
  word <- unlist(strsplit(word, split = ""))
  if ("q" %in% word) {
    check = TRUE
  }
  check
}

q_words <- words_vector[vapply(words_vector, check_q, logical(1))]

q_words_not_correct <- q_words[vapply(q_words, check_duplicate, logical(1))]

### checks if it has duplicate of specific letter
check_q_duplicate <- function(word) {
  check = FALSE
  word <- unlist(strsplit(word, split = ""))
  if (sum(word == "q") > 1) {
    check = TRUE
  }
  check
}

### function that checks if word is duplicate and has specific letter
check_q_both <- function(word) {
  check = FALSE
  if (check_duplicate(word) && check_q_duplicate(word)) {
    check = TRUE
  }
  check
}

### finds proportion
q_prop <- length(q_words[vapply(q_words, check_q_both, logical(1))]) / length(q_words)

### adds proportion to df
proportions_df[17 , 2] <- q_prop

############ r #################################################################

### checks if word has specific letter
check_r <- function(word) {
  check = FALSE
  word <- unlist(strsplit(word, split = ""))
  if ("r" %in% word) {
    check = TRUE
  }
  check
}

r_words <- words_vector[vapply(words_vector, check_r, logical(1))]

r_words_not_correct <- r_words[vapply(r_words, check_duplicate, logical(1))]

### checks if it has duplicate of specific letter
check_r_duplicate <- function(word) {
  check = FALSE
  word <- unlist(strsplit(word, split = ""))
  if (sum(word == "r") > 1) {
    check = TRUE
  }
  check
}

### function that checks if word is duplicate and has specific letter
check_r_both <- function(word) {
  check = FALSE
  if (check_duplicate(word) && check_r_duplicate(word)) {
    check = TRUE
  }
  check
}

### finds proportion
r_prop <- length(r_words[vapply(r_words, check_r_both, logical(1))]) / length(r_words)

### adds proportion to df
proportions_df[18 , 2] <- r_prop

############ s #################################################################

### checks if word has specific letter
check_s <- function(word) {
  check = FALSE
  word <- unlist(strsplit(word, split = ""))
  if ("s" %in% word) {
    check = TRUE
  }
  check
}

s_words <- words_vector[vapply(words_vector, check_s, logical(1))]

s_words_not_correct <- s_words[vapply(s_words, check_duplicate, logical(1))]

### checks if it has duplicate of specific letter
check_s_duplicate <- function(word) {
  check = FALSE
  word <- unlist(strsplit(word, split = ""))
  if (sum(word == "s") > 1) {
    check = TRUE
  }
  check
}

### function that checks if word is duplicate and has specific letter
check_s_both <- function(word) {
  check = FALSE
  if (check_duplicate(word) && check_s_duplicate(word)) {
    check = TRUE
  }
  check
}

### finds proportion
s_prop <- length(s_words[vapply(s_words, check_s_both, logical(1))]) / length(s_words)

### adds proportion to df
proportions_df[19 , 2] <- s_prop

############ t #################################################################

### checks if word has specific letter
check_t <- function(word) {
  check = FALSE
  word <- unlist(strsplit(word, split = ""))
  if ("t" %in% word) {
    check = TRUE
  }
  check
}

t_words <- words_vector[vapply(words_vector, check_t, logical(1))]

t_words_not_correct <- t_words[vapply(t_words, check_duplicate, logical(1))]

### checks if it has duplicate of specific letter
check_t_duplicate <- function(word) {
  check = FALSE
  word <- unlist(strsplit(word, split = ""))
  if (sum(word == "t") > 1) {
    check = TRUE
  }
  check
}

### function that checks if word is duplicate and has specific letter
check_t_both <- function(word) {
  check = FALSE
  if (check_duplicate(word) && check_t_duplicate(word)) {
    check = TRUE
  }
  check
}

### finds proportion
t_prop <- length(t_words[vapply(t_words, check_t_both, logical(1))]) / length(t_words)

### adds proportion to df
proportions_df[20 , 2] <- t_prop

############ u #################################################################

### checks if word has specific letter
check_u <- function(word) {
  check = FALSE
  word <- unlist(strsplit(word, split = ""))
  if ("u" %in% word) {
    check = TRUE
  }
  check
}

u_words <- words_vector[vapply(words_vector, check_u, logical(1))]

u_words_not_correct <- u_words[vapply(u_words, check_duplicate, logical(1))]

### checks if it has duplicate of specific letter
check_u_duplicate <- function(word) {
  check = FALSE
  word <- unlist(strsplit(word, split = ""))
  if (sum(word == "u") > 1) {
    check = TRUE
  }
  check
}

### function that checks if word is duplicate and has specific letter
check_u_both <- function(word) {
  check = FALSE
  if (check_duplicate(word) && check_u_duplicate(word)) {
    check = TRUE
  }
  check
}

### finds proportion
u_prop <- length(u_words[vapply(u_words, check_u_both, logical(1))]) / length(u_words)

### adds proportion to df
proportions_df[21 , 2] <- u_prop

############ v #################################################################

### checks if word has specific letter
check_v <- function(word) {
  check = FALSE
  word <- unlist(strsplit(word, split = ""))
  if ("v" %in% word) {
    check = TRUE
  }
  check
}

v_words <- words_vector[vapply(words_vector, check_v, logical(1))]

v_words_not_correct <- v_words[vapply(v_words, check_duplicate, logical(1))]

### checks if it has duplicate of specific letter
check_v_duplicate <- function(word) {
  check = FALSE
  word <- unlist(strsplit(word, split = ""))
  if (sum(word == "v") > 1) {
    check = TRUE
  }
  check
}

### function that checks if word is duplicate and has specific letter
check_v_both <- function(word) {
  check = FALSE
  if (check_duplicate(word) && check_v_duplicate(word)) {
    check = TRUE
  }
  check
}

### finds proportion
v_prop <- length(v_words[vapply(v_words, check_v_both, logical(1))]) / length(v_words)

### adds proportion to df
proportions_df[22 , 2] <- v_prop

############ w #################################################################

### checks if word has specific letter
check_w <- function(word) {
  check = FALSE
  word <- unlist(strsplit(word, split = ""))
  if ("w" %in% word) {
    check = TRUE
  }
  check
}

w_words <- words_vector[vapply(words_vector, check_w, logical(1))]

w_words_not_correct <- w_words[vapply(w_words, check_duplicate, logical(1))]

### checks if it has duplicate of specific letter
check_w_duplicate <- function(word) {
  check = FALSE
  word <- unlist(strsplit(word, split = ""))
  if (sum(word == "w") > 1) {
    check = TRUE
  }
  check
}

### function that checks if word is duplicate and has specific letter
check_w_both <- function(word) {
  check = FALSE
  if (check_duplicate(word) && check_w_duplicate(word)) {
    check = TRUE
  }
  check
}

### finds proportion
w_prop <- length(w_words[vapply(w_words, check_w_both, logical(1))]) / length(w_words)

### adds proportion to df
proportions_df[23 , 2] <- w_prop

############ x #################################################################

### checks if word has specific letter
check_x <- function(word) {
  check = FALSE
  word <- unlist(strsplit(word, split = ""))
  if ("x" %in% word) {
    check = TRUE
  }
  check
}

x_words <- words_vector[vapply(words_vector, check_x, logical(1))]

x_words_not_correct <- x_words[vapply(x_words, check_duplicate, logical(1))]

### checks if it has duplicate of specific letter
check_x_duplicate <- function(word) {
  check = FALSE
  word <- unlist(strsplit(word, split = ""))
  if (sum(word == "x") > 1) {
    check = TRUE
  }
  check
}

### function that checks if word is duplicate and has specific letter
check_x_both <- function(word) {
  check = FALSE
  if (check_duplicate(word) && check_x_duplicate(word)) {
    check = TRUE
  }
  check
}

### finds proportion
x_prop <- length(x_words[vapply(x_words, check_x_both, logical(1))]) / length(x_words)

### adds proportion to df
proportions_df[24 , 2] <- x_prop

############ y #################################################################

### checks if word has specific letter
check_y <- function(word) {
  check = FALSE
  word <- unlist(strsplit(word, split = ""))
  if ("y" %in% word) {
    check = TRUE
  }
  check
}

y_words <- words_vector[vapply(words_vector, check_y, logical(1))]

y_words_not_correct <- y_words[vapply(y_words, check_duplicate, logical(1))]

### checks if it has duplicate of specific letter
check_y_duplicate <- function(word) {
  check = FALSE
  word <- unlist(strsplit(word, split = ""))
  if (sum(word == "y") > 1) {
    check = TRUE
  }
  check
}

### function that checks if word is duplicate and has specific letter
check_y_both <- function(word) {
  check = FALSE
  if (check_duplicate(word) && check_y_duplicate(word)) {
    check = TRUE
  }
  check
}

### finds proportion
y_prop <- length(y_words[vapply(y_words, check_y_both, logical(1))]) / length(y_words)

### adds proportion to df
proportions_df[25 , 2] <- y_prop

############ z #################################################################

### checks if word has specific letter
check_z <- function(word) {
  check = FALSE
  word <- unlist(strsplit(word, split = ""))
  if ("z" %in% word) {
    check = TRUE
  }
  check
}

z_words <- words_vector[vapply(words_vector, check_z, logical(1))]

z_words_not_correct <- z_words[vapply(z_words, check_duplicate, logical(1))]

### checks if it has duplicate of specific letter
check_z_duplicate <- function(word) {
  check = FALSE
  word <- unlist(strsplit(word, split = ""))
  if (sum(word == "z") > 1) {
    check = TRUE
  }
  check
}

### function that checks if word is duplicate and has specific letter
check_z_both <- function(word) {
  check = FALSE
  if (check_duplicate(word) && check_z_duplicate(word)) {
    check = TRUE
  }
  check
}

### finds proportion
z_prop <- length(z_words[vapply(z_words, check_z_both, logical(1))]) / length(z_words)

### adds proportion to df
proportions_df[26 , 2] <- z_prop

# Final props df
proportions_df
```
